\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-10 latex/paper_sensores/paper.tex
mas cosas del paper de los sensores

The calibration proposed in this paper is tested on an accelerometer ADXL345 of Analog Devices and a gyroscope ITG-3200  of InvenSense, yet the model developed and the methodology can be used in other devices because the model is based on comun characteristics of MEMS sensors.\\

@@

>>>>

The calibration proposed in this paper is tested on a 3-axis accelerometer ADXL345 of Analog Devices and a 3-axis gyroscope ITG-3200  of InvenSense, yet the model developed and the methodology can be used in other devices because the model is based on comun characteristics of MEMS sensors. The sensors named before are included in a Inertial Measurment Unit(IMU): The Mongoose(figure \ref{fig:mongoose}). \\

@@

As it was stated before, there exist many error sources in MEMS devices. In \cite{bib:calib_imu} two of this sources are mentioned: the nonlinear response of the sensors and the non-orthogonality of the axis of the sensor. In addition we can observe also that it exist an electric noise in the measures (figure \ref{fig:ruido}) and a dependance of the temperature.\\

In the datasheets of the considered sensors(\cite{bib:acc_data} and \cite{bib:gyro_data}) the effect of nonlinearityis negligible since it represents the $\pm 0.5.\%$  of the full scale for the accelerometer and the $\pm 0.2\%$ for the gyroscope. Therefore we will not discuss any further on this issue.\\
%TODO Esto es medio turbio que sea despreciable... en realidad me da que no habría que despreciarlo. Capaz que es mejor esconder este punto.

In figure \ref{fig:ruido} we can observe that the electrical noise of the devices is typically 2 bits, this error (acording the datashets \cite{bib:acc_data} and \cite{bib:gyro_data})correspond to $7.8 mg$ and $0.14 ^{\circ}/s $.  
%TODO Cuando tengamos la gráfica ver bien cuanto es el ruido y a cuanto corresponde en la vida real. Tampoco se si es tan despreciable. Capaz que hay que decir que se usan muchas muestras normalmente y que variaciones aleatorias de cierta varianza no joden mucho. Pero ahora no me voy a poner a hacer eso xq tengo sueño.
